---
title: "LME_report"
output: html_document
date: "2024-06-28"
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sjPlot)
library(ggplot2)
library(flexplot)
library(here)
```
# Load The Data
```{r, echo=FALSE}
load(here("output","Strategic_Models","all_average_by_trial.RData"))
all_average_by_trial <- average_by_trial
load(here("output","Strategic_Models","no_haptic_average_by_trial.RData"))
no_haptic_average_by_trial <- average_by_trial
print('Done')
```

# Load All Models
```{r, echo=FALSE}
load(here("output","Strategic_Models","all_models.RData"))
all_models <- models
load(here("output","Strategic_Models","no_haptic_models.RData"))
no_haptic_models <- models
print('Done')
```

# Everything Model
```{r, echo=FALSE, message=FALSE}
model <- all_models[[1]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)
```

# Base Model
```{r, include=FALSE}
model <- all_models[[2]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)
print('Done')
```

# Time ~ Haptic
```{r, echo=FALSE}
model <- all_models[[3]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ haptic)
```

# Time ~ Visual
```{r, echo=FALSE}
model <- all_models[[4]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ visual)
```

# Time ~ Haptic * Visual 
```{r, echo=FALSE}
model <- all_models[[5]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ haptic + visual)
```

# Time ~ Collaborative
```{r, echo=FALSE}
model <- all_models[[6]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ collaborative)
```

# Time ~ Haptic * Visual * Collaborative (Not a good model)
```{r, echo=FALSE}
model <- all_models[[7]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

# flexplot(data = all_average_by_trial, time_through_maze ~ visual)
```

# Time ~ Haptic * Visual * Path Length
```{r, echo=FALSE}
model <- all_models[[8]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ path_length, method = 'lm')
flexplot(data = all_average_by_trial, time_through_maze ~ visual + path_length)
flexplot(data = all_average_by_trial, time_through_maze ~ haptic + path_length)

```

# Time ~ Map
```{r, echo=FALSE}
model <- all_models[[9]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ map_factor)
```

# Time ~ Visual * Haptic * Map (possible)
```{r, echo=FALSE}
model <- all_models[[10]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ visual + map_factor)

```

# Path Length ~ Map
```{r, echo=FALSE}
model <- all_models[[11]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, path_length ~ map_factor)

```

# Everything Model (Only Haptic - not a good model)
```{r, echo=FALSE}
model <- no_haptic_models[[1]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = no_haptic_average_by_trial, time_through_maze ~ visual)
```

# Base (Only Haptic)
```{r, echo=FALSE, include=FALSE}
model <- no_haptic_models[[2]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

print("Done")
```

# Time ~ Visual (Only Haptic)
```{r, echo=FALSE}
model <- no_haptic_models[[3]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = no_haptic_average_by_trial, time_through_maze ~ visual)
```

# Time ~ Collaborative (Only Haptic)
```{r, echo=FALSE}
model <- no_haptic_models[[4]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ collaborative)
```

# Time ~ Visual * Collaborative (Only Haptic - not a good model)
```{r, echo=FALSE}
model <- no_haptic_models[[5]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ collaborative)
```

# Time ~ Visual * Path Length (Only Haptic - nothing new here)
```{r, echo=FALSE}
model <- no_haptic_models[[6]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

#flexplot(data = all_average_by_trial, time_through_maze ~ path_length, method='lm')
```

# Time ~ Map (Only Haptic - nothing new here)
```{r, echo=FALSE}
model <- no_haptic_models[[7]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

#flexplot(data = all_average_by_trial, time_through_maze ~ collaborative)
```

# Time ~ Visual * Map (Only Haptic - nothing new here)
```{r, echo=FALSE}
model <- no_haptic_models[[8]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ collaborative)
```

# Time ~ Visual * Map + Collaborative (Only Haptic - not a good model)
```{r, echo=FALSE}
model <- no_haptic_models[[9]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ collaborative)
```

# Path Length ~ Collaborative (Only Haptic)
```{r, echo=FALSE}
model <- no_haptic_models[[10]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, path_length ~ collaborative)
```

# Path Length ~ Visual * Collaborative (Only Haptic - not a good model)
```{r, echo=FALSE}
model <- no_haptic_models[[11]]
f <- formula(model)
print(f)
s <- summary(model)
print(s)

flexplot(data = all_average_by_trial, time_through_maze ~ collaborative)
```

